Viscous Erosion in Porous Media

### 2018-03-15 docs/methods/erosion_methods.tex
I took a shot at the abstract.

\begin{abstract} 
We consider two dimensional eroding bodies in Stokes flow
\end{abstract}

>>>>

\begin{abstract} 
We develop numerical methods to simulate the fluid-mechanical erosion of many bodies (order 50) in 2D Stokes flow. The broad aim is to simulate the erosion of a porous medium (e.g.~ground water flow) with resolution at the grain scale. Our fluid solver is based on a boundary-integral formulation of the Stokes equations with a double-layer potential. We solve the associated linear system iteratively with GMRES and use the fast-multipole method (FMM) for acceleration. Since the underlying integral equation is second-kind, GMRES achieves a bounded iteration count (independent of the number of unknowns). To evolve the individual grains under shear-driven erosion, we regularize via curvature-penalization and solve the associated system using the {\thL} formulation. This framework allows numerically stable treatment of stiff terms and thus permits large time steps. The overall accuracy of our method is exponential in space and second-order in time. The method is computationally efficient, with the main part of the solver having an $O(N)$ cost, and a one-time $O(N^2)$ computation. We benchmark single-body results against analytical predictions. In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact. The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
\end{abstract}
